Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-17 analysis/paper/paper.Rmd
Remove table 3, redundant with text

Depending on the scoring event, three to five of this paper's authors were each assigned to rate a randomised list of journal articles using scoring criteria devised for the purposes of this research (Table \@ref(tab:scoring)) in each of the three different scoring events as their time allowed for their participation.
In the first event, three authors (AS, EDP, and ZF) evaluated 200 articles, in the second event two authors evaluated 100 articles (EDP, KA) and in the third round, five authors (AS, EDP, KA, ZF, NG) evaluated 150 articles for a total of 450 articles.

@@

```{r scoring, echo=FALSE, message=FALSE, warning=FALSE}
readODS::read_ods(
    system.file(
      "extdata",
      "Reproducibility_in_plant_pathology_notes.ods",
      package = "Reproducibility.in.Plant.Pathology"
    ),
    na = "NA",
    sheet = "scoring_criteria_paper"
  ) %>% 
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  autofit() %>%
  set_caption(
    "Articles were three in two areas for reproducibility on a scale of '0' to '3' by five independent evaluators to rank articles in each of two areas, 'Computational Methods Availability' and 'Data Availability'.")
```

>>>>

Depending on the scoring event, three to five of this paper's authors were each assigned to rate a randomised list of journal articles using scoring criteria devised for the purposes of this research in each of the three different scoring events as their time allowed for their participation.
In the first event, three authors (AS, EDP, and ZF) evaluated 200 articles, in the second event two authors evaluated 100 articles (EDP, KA) and in the third round, five authors (AS, EDP, KA, ZF, NG) evaluated 150 articles for a total of 450 articles.

@@
